Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-09-11 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added Summary Tables to Ch 3 and 4
Also added data and new point source graphic

\begin{figure}[p]
  \centering
  \includegraphics[width=3.5in]{../Figures/FHNG_TC_Plume_Avg}\\
  \includegraphics[width=3.5in]{../Figures/FHPUF_TC_Plume_Avg}\\
  \includegraphics[width=3.5in]{../Figures/FHGAS_TC_Plume_Avg}\\
  \caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires. The number following the TC represents the height of thermocouple in decimeters above the surface of the burner.}
  \label{Temp}
\end{figure}

@@

A review of the graphs of the peak average temperatures at the wall, burner centerline array, shows that all of the fuels had at least one thermocouple position with a peak of approximately 500~$^{\circ}$C when the burner was against the wall.  At 0.15~m away from the wall the peak average temperature from this data set was provided by the gasoline fueled fire and it was approximately 350~$^{\circ}$C.  Based on temperature alone, the fires examined would only have the potential to ignite the paper surface of the gypsum wallboard when the burner was in contact with the wall.  The peak average temperatures at the wall, burner edge array, would indicate that the paper may not ignite at the burner edge.  The peak average temperature of approximately 400~$^{\circ}$C was generated by the gasoline fueled fire when the burner was positioned against the wall.

Of course the temperatures of the thermocouples in the wall are a result of the energy transferred to the wall and the thermo-physical properties of the wall material. Assuming that the properties of calcium silicate board and the gypsum board are similar, the heat flux graphs were reviewed to see where the heat flux exceeded 35~kW/m$^2$. All of the fuels generated heat fluxes in excess of 35~kW/m$^2$ at the burner centerline array when the burners were against the wall.  The gasoline and the polyurethane fueled burners also exposed the wall to heat fluxes higher than 35~kW/$^2$ at 0.15~m from the wall.  However only the burner against the wall positions provided a combination of heat flux and temperature that had the potential to ignite the paper on the gypsum wallboard based on the handbook data.

@@

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline Distance from wall  	& Natural Gas 		& Gasoline			& Polyurethane Foam \\
		\hline (m) 					& Number of Tests 	& Number of Tests  	& Number of Tests 	\\
		\hline 0.61 				& 0 				& 1 				& 2 			 	\\
		\hline 0.31					& 3	 				& 1					& 2 			 	\\
		\hline 0.15					& 1				 	& 1					& 2 			 	\\
		\hline 0.08					& 0 				& 1 				& 2 	 			\\
		\hline 0.00					& 1 				& 1 				& 3 	 			\\
		\hline
	\end{tabular}
	\caption[Matrix of instrumented gypsum wallboard experiments]{Matrix of instrumented gypsum wallboard experiments}
	\label{tab:IWGB_experiments}
\end{table}

@@

@@

Needed?
{}
\chapter{Comparison of Algebraic Fire Characterizations with Fire Pattern Results}

>>>>

\begin{figure}[p]
  \centering
  \includegraphics[width=3.5in]{../Figures/FHNG_TC_Plume_Avg}\\
  \includegraphics[width=3.5in]{../Figures/FHGAS_TC_Plume_Avg}\\
  \includegraphics[width=3.5in]{../Figures/FHPUF_TC_Plume_Avg}\\
  \caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires. The number following the TC represents the height of thermocouple in decimeters above the surface of the burner.}
  \label{Temp}
\end{figure}

@@

A summary of the peak average temperatures and heat fluxes at the non-combustible wall is provided in Table~\ref{tab:TW_Summary}.   Based on the temperature criteria for igniting gyspum wallboard, found in the literature, only the gasoline and polyurethane foam burners positioned against the wall provided temperatures in excess of 515~$^{\circ}$C.  Based on heat flux, each of the burners exceeded the 26~kW/m$^2$ ignition criteria, when positioned against the wall and at when the edge of the burner was 0.15~m away from the wall.

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline {Burner} & \multicolumn{2}{c}{Natural Gas} & \multicolumn{2}{c}{Gasoline} & \multicolumn{2}{c|}{PU Foam} \\
		\hline  Position & Temp~(C) & HF~(kW/m$^{2}$) & Temp~(C) & HF~(kW/m$^{2}$) & Temp~(C) & HF~(kW/m$^{2}$) 	\\
		\hline \hline 0.61~m & 95 & 5 & 106 & 7 & 71 & 6 \\
		\hline 0.31~m & 164 & 14 & 232 & 24 & 148 & 16	\\
		\hline 0.15~m & 257 & 33 & 356 & 45 & 266 & 39	\\
		\hline 0.00~m & 487 & 43 & 621 & 70 & 526 & 65 	\\
		\hline
	\end{tabular}
	\caption[Summary of instrumented non-combustible wall experiments]{Summary of peak temperatures and heat fluxes from the instrumented non-combustible wall experiments}
	\label{tab:TW_Summary}
\end{table}

Of course the temperatures of the thermocouples in the wall are a result of the energy transferred to the wall and the thermo-physical properties of the wall material. The properties of the calcium silicate board are simlar but not identical to gypsum wallboard.  The heat flux data is independent of the wall material, so it may be a better predictor of the fire damage to gypsum wallboard when exposed to the burners at different distances.    All of the fuels generated heat fluxes in excess of 26~kW/m$^2$.  However only the burner against the wall positions provided a combination of heat flux and temperature that had the potential to ignite the paper on the gypsum wallboard based on the handbook data.  The experiments conducted with the instrumented gypsum wall board will provide data for comparsion with data provided in this chapter and provide insight in to where the gypsum wall board ignites.

@@

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline Distance from wall  	& Natural Gas 		& Gasoline			& Polyurethane Foam \\
		\hline (m) 					& Number of Tests 	& Number of Tests  	& Number of Tests 	\\
		\hline 0.61 				& 1 				& 1 				& 2 			 	\\
		\hline 0.31					& 3	 				& 1					& 2 			 	\\
		\hline 0.15					& 1				 	& 1					& 2 			 	\\
		\hline 0.08					& 0 				& 1 				& 2 	 			\\
		\hline 0.00					& 1 				& 1 				& 3 	 			\\
		\hline
	\end{tabular}
	\caption[Matrix of instrumented gypsum wallboard experiments]{Matrix of instrumented gypsum wallboard experiments}
	\label{tab:IWGB_experiments}
\end{table}

@@

A summary of the peak average temperatures and heat fluxes at the wall is provided in Table~\ref{tab:IWGB_Summary}.

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline {Burner} & \multicolumn{2}{c}{Natural Gas} & \multicolumn{2}{c}{Gasoline} & \multicolumn{2}{c|}{PU Foam} \\
		\hline  Position & Temp~(C) & HF~(kW/m$^{2}$) & Temp~(C) & HF~(kW/m$^{2}$) & Temp~(C) & HF~(kW/m$^{2}$) 	\\
		\hline \hline 0.61~m & 132 & 4 & 109 & 6 & 76 & 4 \\
		\hline 0.31~m & 160 & 11 & 185 & 18 & 151 & 12	\\
		\hline 0.15~m & 250 & 23 & 377 & 57 & 244 & 25	\\
		\hline 0.00~m & 539 & 55 & 590 & 61 & 415 & 59 	\\
		\hline
	\end{tabular}
	\caption[Summary of instrumented gypsum wallboard experiments]{Summary of peak temperatures and heat fluxes from the instrumented gypsum wallboard experiments}
	\label{tab:IWGB_Summary}
\end{table}

@@

Needed?

{}
\chapter{Comparison of Algebraic Fire Characterizations with Fire Pattern Results}
